Offshore Modeling - Manuscript Model

### 2020-02-15 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
figure changes

#Format ggplot for rest of document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), 
                             panel.grid.minor = element_blank(), 
                             panel.border = element_rect(fill = NA),
                             axis.text = element_text(size = 12, color = "black"),
                             axis.title = element_text(size = 14, color = "black")))

@@

year_plot <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `Mean Catch`)) +
    geom_errorbar(aes(x = survey_year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))
  )

@@

```{r, fig.height=4}
year_foa <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `% Occurrence`)) +
    scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
    labs(x = NULL, y = "Percent occurrence")

@@

# Plot
rs_plot <- rs_summary %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA))

@@

```{r, fig.height=4}
rs_plot_2 <- rs_foa %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray50"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA))

@@

```{r fig.height=4}
rs_plot + rs_plot_2

@@

## Catch per Hectare Plot

@@

#Drop Infinite credibility intervals
best_mod_dat <- best_mod_dat %>% 
  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL))

# Catch Plot
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
      geom_line(aes(year_n, response, color = season)) +
      geom_point(aes(year_n, response, color = season, shape = season)) +
      scale_color_grey(start = 0.2, end = 0.6) + 
      labs(
        x = NULL, 
        y = "Crabs per Hectare",
        title = "Model Estimates and Yearly observed means") +
      facet_grid(region ~ .) +
  theme(
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank())
p

@@

```{r}
####  Sampling Effort  ####
ggplot() +
  geom_stars(data = effort_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom")
```

@@

####  CPUE  ####
ggplot() +
  geom_stars(data = cpue_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom")

@@

```{r}
####  Total Catch  ####
ggplot() +
  geom_stars(data = catch_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total C. sapidus Caught",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom")

>>>>

#Format ggplot for rest of document
theme_set(theme_bw() + 
          theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.border = element_rect(fill = NA),
            axis.text = element_text(size = 12, color = "black"),
            axis.title = element_text(size = 12, color = "black"),
            legend.text = element_text(size = 12, color = "black"),
            legend.background = element_rect(fill = NA))
          )

@@

west_mean <- round(mean(seamap_west$cpue_towspd, na.rm = T), 3)

year_plot <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `Mean Catch`), fill = "gray35") +
    geom_errorbar(aes(x = survey_year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  geom_hline(yintercept = west_mean, 
             linetype = "dashed") +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))
  )

@@

```{r, fig.height=4}
west_foa <- round(mean(seamap_west$crab_presence, na.rm = TRUE), 3)

year_foa <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `% Occurrence`)) +
    geom_hline(yintercept = west_foa, 
               linetype = "dashed") +
    scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
    labs(x = NULL, y = "Percent occurrence")

@@

# Plot
rs_plot <- rs_summary %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

```{r, fig.height=4}
rs_plot_2 <- rs_foa %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

```{r fig.height=4}
rs_plot <- rs_plot + theme(legend.position = "none")
rs_plot + rs_plot_2

@@

## Catch per Hectare Plot {.tabset .tabset-pills}

### Seasonal Prediction Differences

@@

#Drop Infinite credibility intervals
best_mod_dat <- best_mod_dat %>% 
  mutate(asymp.UCL = ifelse(asymp.UCL == Inf, NA, asymp.UCL),
         season = factor(season, levels = c("Summer", "Fall")),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight")))

# Catch Plot
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
      geom_line(aes(year_n, response, color = season)) +
      geom_point(aes(year_n, response, color = season, shape = season)) +
      scale_color_grey(start = 0.35, end = 0.7) + 
      labs(
        x = NULL, 
        y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
      facet_grid(region ~ .) +
  theme(
    legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank())
p

### Observed vs. Predicted Data

```{r}
#Observed data
mean_obs <- mean(seamap_west$cpue_towspd)
obs_timeline <- seamap_west %>% 
  group_by(survey_year, region, season) %>% 
  summarise(Nobs = n(),
            PercentPos = mean(crab_presence),
            Mean_CPUE = mean(cpue_towspd)) %>% 
  ungroup() %>% 
  mutate(season = factor(season, levels = c("Summer", "Fall")),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight")),
         Index_Obs = Mean_CPUE/mean_obs)

#Overall group means
panel_means <- seamap_west %>% 
  group_by(region, season) %>% 
  summarise(Mean_CPUE = mean(cpue_towspd))

#ggplot of standardized index of abundance
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
    geom_hline(data = panel_means, 
               aes(yintercept = Mean_CPUE), alpha = 0.5) +
    # geom_ribbon(aes(year_n, 
    #                 ymin = asymp.LCL, 
    #                 ymax = asymp.UCL), 
    #             fill = "gray80") +
    geom_line(aes(x = year_n, 
                  y = response, 
                  group = 1, 
                  col = "Predicted")) +
    geom_point(aes(x = year_n, 
                   y = response, 
                   col = "Predicted")) +
    # Observed Data
    geom_line(data = obs_timeline, 
            aes(x = survey_year, 
                y = Mean_CPUE, 
                group = region, 
                col = "Observed"), linetype = 2) +
    geom_point(data = obs_timeline, 
               aes(x = survey_year, 
                   y = Mean_CPUE, 
                   group = region, 
                   col = "Observed")) +
    #Theme changes
    #scale_color_grey(start = 0.35, end = 0.7) + 
    scale_color_manual(values = c("gray35", "royalblue")) + 
    labs(
      x = NULL, 
      y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
  theme(legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank()) +
  facet_grid(season~region)
p

@@

```{r}
####  Sampling Effort  ####
ggplot() +
  geom_stars(data = effort_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12))
```

@@

####  CPUE  ####
ggplot() +
  geom_stars(data = cpue_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12))

@@

```{r}
####  Total Catch  ####
ggplot() +
  geom_stars(data = catch_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total C. sapidus Caught",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12))
